---
title: ' Geo Location Wise Retail and Online Sale Visualization'
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

Geo-Specific Visualization of Retail and Online Sales

```{r}
library(ggmap)
library(ggplot2)
library(zipcode)

data_dc <- read.delim(file='//10.8.8.51/lv0/Move to Box/Mithun/projects/9.BR_US_DS_Project/1.data/BR_disc_sens_geo_data.txt',
                      sep = '|',header = F, col.names = c('customer_key',
'percent_disc_last_12_mth',
'br_net_sales_amt_12_mth',
'flag_employee',
'addr_zip_code',
'resp_disc_percent',
'browse_hit_ind_tot',
'purchased',
'br_online_sales12_mth',
'br_offline_sales_12mth'))

data_dc$br_retail_percent <-  data_dc$br_offline_sales_12mth / data_dc$br_net_sales_amt_12_mth

data_dc$br_online_percent <-  data_dc$br_online_sales12_mth / data_dc$br_net_sales_amt_12_mth

data_dc$br_gross_sales_amt <-  data_dc$br_net_sales_amt_12_mth / (1 - data_dc$percent_disc_last_12_mth)

```
Plot Data as per PIN code
```{r}
library(dplyr)
zip_wise_data <- data_dc[,c("br_offline_sales_12mth","br_online_sales12_mth","br_net_sales_amt_12_mth","br_gross_sales_amt","addr_zip_code")] %>% group_by(addr_zip_code) %>% summarise(br_online_sales12_mth = sum(br_online_sales12_mth,na.rm=T), br_offline_sales_12mth = sum(br_offline_sales_12mth,na.rm=T), br_net_sales_amt_12_mth = sum(br_net_sales_amt_12_mth,na.rm=T), br_gross_sales_amt = sum(br_gross_sales_amt,na.rm=T))

zip_wise_data <- zip_wise_data[zip_wise_data$addr_zip_code!='',]


library(zipcode)
data("zipcode")
data_dc2<- inner_join(data_dc,zipcode,by=c("addr_zip_code"="zip"))
library("ggplot2")

zip_wise_data <- left_join(zipcode,zip_wise_data,by=c("zip"="addr_zip_code"))
```
Discount Rate by ZipCode

```{r}
zip_wise_data$disc_percent <- (1 - zip_wise_data$br_net_sales_amt_12_mth/zip_wise_data$br_gross_sales_amt )
zip_wise_data$disc_percent[is.na(zip_wise_data$disc_percent)] <- 0
zip_wise_data$disc_percent[zip_wise_data$disc_percent > 1] <- 1
zip_wise_data$disc_percent[zip_wise_data$disc_percent < 0] <- 0

zip_wise_data$Online_percent<-zip_wise_data$br_online_sales12_mth/zip_wise_data$br_net_sales_amt_12_mth
zip_wise_data$Online_percent[is.na(zip_wise_data$Online_percent)] <- 0
zip_wise_data$Online_percent[zip_wise_data$Online_percent > 1] <- 1
zip_wise_data$Online_percent[zip_wise_data$Online_percent < 0] <- 0

zip_wise_data$binx <- cut(zip_wise_data$disc_percent,breaks = c(-Inf,0,0.20,0.35,0.40,Inf),include.lowest = T,
                          labels = c("No_Info","a_Low","b_Medium","c_High","d_VeryHigh"))


zip_wise_data <-zip_wise_data[which(zip_wise_data$latitude < 50 & zip_wise_data$latitude > 25 &
                                    zip_wise_data$longitude > -125 &  zip_wise_data$longitude < -66),]
ggplot(data=zip_wise_data) + geom_point(aes(x=longitude, y=latitude, colour=binx)) +ggtitle(" Discount Rate  ZIPCODE wise") +theme(legend.position ="bottom")

ggplot(zip_wise_data, aes(x = longitude, y = latitude,  fill= disc_percent )) + geom_polygon(colour = "white", size = 0.1) + theme(legend.position ="bottom")

ggplot(zip_wise_data, aes(x = longitude, y = latitude,  fill= Online_percent )) + geom_polygon(colour = "white", size = 0.1) + theme(legend.position ="bottom")

```
Discount Bin 10 is highest Discount
```{r}
require(ggplot2)
require(maptools)
mapcounties <- map_data("county")
mapstates <- map_data("state")

counties <- map('county', fill=TRUE, col="transparent", plot=FALSE)
IDs <- sapply(strsplit(counties$names, ":"), function(x) x[1])
counties_sp <- map2SpatialPolygons(counties, IDs=IDs,
                                   proj4string=CRS("+proj=longlat +datum=WGS84"))

pointsSP <- SpatialPoints(as.data.frame(zip_wise_data[,c('longitude','latitude')]),
proj4string=CRS("+proj=longlat +datum=WGS84"))
indices <- over(pointsSP, counties_sp)

countyNames <- sapply(counties_sp@polygons, function(x) x@ID)

zip_wise_data$county<-countyNames[indices]
# Generate Comma Separated County/Subregion list for all Counties of US
#
mapcounties$county <- with(mapcounties , paste(region, subregion, sep = ","))

# Aggregate our data at County Level (it was earlier aggreated at zipcode level)
#
zip_wise_data.sum<- zip_wise_data %>% group_by(county) %>%  summarize(br_online_sales12_mth = sum(br_online_sales12_mth,na.rm=T), br_offline_sales_12mth = sum(br_offline_sales_12mth,na.rm=T), br_net_sales_amt_12_mth = sum(br_net_sales_amt_12_mth,na.rm=T), br_gross_sales_amt = sum(br_gross_sales_amt,na.rm=T),disc_percent=median(disc_percent,na.rm=T),Online_percent=median(Online_percent))


# Remove any duplicate records
#
zip_wise_data.un<-zip_wise_data.sum[!duplicated(zip_wise_data[c("county")]),]

zip_wise_data.final=merge(zip_wise_data.sum,zip_wise_data.un,by.x='county',by.y = 'county')

zip_wise_data.final$disc_perc_bin <- as.factor(ntile(zip_wise_data.final$disc_percent.x,5))
# Merge our data with all US counties data
#
zip_wise_data.final$Online_percent_bin <- as.factor(ntile(zip_wise_data.final$Online_percent.x,5))
mergedata <- merge(mapcounties, zip_wise_data.final, by.x = "county", by.y = "county")
```
High Discount Rate County Wise
```{r}
map <- ggplot(mergedata, aes(long,lat,group=group)) + geom_polygon(aes(fill=disc_perc_bin)) 
map <- map+theme(panel.background = element_rect(fill = "white"),legend.position = "bottom",
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())
map <- map + geom_path(data = mapstates, colour = "black", size = .3)
map <- map + geom_path(data = mapcounties, colour = "red", size = .5, alpha = .1)  +
  expand_limits(x = mergedata$long, y = mergedata$lat)
map


```
High Online Sale Percent County Wise

```{r}
ggplot(mergedata, aes(long,lat,group=group)) + geom_polygon(aes(fill=Online_percent_bin)) + theme(panel.background = element_rect(fill = "white"),legend.position = "bottom",
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank()) + geom_path(data = mapstates, colour = "black", size = .3) + geom_path(data = mapcounties, colour = "red", size = .5, alpha = .1)  +
  expand_limits(x = mergedata$long, y = mergedata$lat)

```
Statewide map
```{r}

states_map <-map_data("state")
head(states_map)
library(sqldf)

data_dc3 <-  left_join(zipcode[,c("zip","state")],data_dc2,by=c("zip"="addr_zip_code"))

require(dplyr)
zip_wise_data_state <- data_dc2 %>% group_by(state) %>% summarise(br_online_sales12_mth = sum(br_online_sales12_mth,na.rm=T), br_offline_sales_12mth = sum(br_offline_sales_12mth,na.rm=T), br_net_sales_amt_12_mth = sum(br_net_sales_amt_12_mth,na.rm=T), br_gross_sales_amt = sum(br_gross_sales_amt,na.rm=T))

st_code_file<- data.frame(full_name=c('alabama','alaska','arizona','arkansas','california','colorado',
                                      'connecticut',	'delaware',	'district of columbia',	'florida',	'georgia',
                                      'hawaii',	'idaho',	'illinois',	'indiana',	'iowa',	'kansas',	'kentucky',	
                                      'louisiana',	'maine',	'maryland',	'massachusetts',	'michigan',	'minnesota',
                                      'mississippi',	'missouri',	'montana',	'nebraska',	'nevada',	'new hampshire',
                                      'new jersey',	'new mexico',	'new york',	'north carolina',	'north dakota',	
                                      'ohio',	'oklahoma',	'oregon',	'pennsylvania',	'rhode island',	'south carolina',
                                      'south dakota',	'tennessee',	'texas',	'utah',	'vermont',	'virginia',	'washington',
                                      'west virginia',	'wisconsin',	'wyoming'),
                          state_code=c('AL',	'AK',	'AZ',	'AR',	'CA',	'CO',	'CT',	'DE',	'DC',	'FL',	'GA',	'HI',	'ID',	'IL',
                                       'IN',	'IA',	'KS',	'KY',	'LA',	'ME',	'MD',	'MA',	'MI',	'MN',	'MS',	'MO',	'MT',	'NE',
                                       'NV',	'NH',	'NJ',	'NM',	'NY',	'NC',	'ND',	'OH',	'OK',	'OR',	'PA',	'RI',	'SC',	'SD',
                                       'TN',	'TX',	'UT',	'VT',	'VA',	'WA',	'WV',	'WI',	'WY'))

zip_wise_data_state <- inner_join(st_code_file,zip_wise_data_state,by=c("state_code"="state"))

zip_wise_data_state$disc_percent <- (1 - zip_wise_data_state$br_net_sales_amt_12_mth/zip_wise_data_state$br_gross_sales_amt )
zip_wise_data_state$disc_percent[is.na(zip_wise_data_state$disc_percent)] <- 0
zip_wise_data_state$disc_percent[zip_wise_data_state$disc_percent > 1] <- 1
zip_wise_data_state$disc_percent[zip_wise_data_state$disc_percent < 0] <- 0

zip_wise_data_state$Online_percent <- zip_wise_data_state$br_online_sales12_mth/zip_wise_data_state$br_net_sales_amt_12_mth
zip_wise_data_state$Online_percent[is.na(zip_wise_data_state$Online_percent)] <- 0
zip_wise_data_state$Online_percent[zip_wise_data_state$Online_percent > 1] <- 1
zip_wise_data_state$Online_percent[zip_wise_data_state$Online_percent < 0] <- 0


```
 Discount and % of Online Sales Visualization by State 
```{r}
zip_wise_data_state2 <- zip_wise_data_state[,c("full_name","disc_percent","Online_percent")]
names(zip_wise_data_state2) <- c("state","disc_percent","Online_percent")


ggplot(zip_wise_data_state2, aes(map_id = state)) +
  geom_map(aes(fill = disc_percent), map = states_map, color ="black") +
  expand_limits(x = states_map$long, y = states_map$lat) +
  theme(legend.position = "bottom",
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank()) +
  scale_fill_gradient(low="green", high="red") +
  guides(fill = guide_colorbar(barwidth = 10, barheight = 1))
```
% Online Sales by State
```{r}
ggplot(zip_wise_data_state2, aes(map_id = state)) +
  geom_map(aes(fill = Online_percent), map = states_map, color ="black") +
  expand_limits(x = states_map$long, y = states_map$lat) +
  theme(legend.position = "bottom",
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank()) +
  scale_fill_gradient(low="green", high="red") 
  guides(fill = guide_colorbar(barwidth = 10, barheight = .5))
```

Discount  Percent taken accross United States
```{r}
require(leaflet)

leaflet(zip_wise_data) %>% addTiles() %>%
  addCircles(lng = ~longitude, lat = ~latitude, weight = 1,
             radius = ~(disc_percent-0.3)*100, popup = ~city  )
```

Online Sale Percent over overall sales accross United States

```{r}
require(leaflet)

leaflet(zip_wise_data) %>% addTiles() %>%
  addCircles(lng = ~longitude, lat = ~latitude, weight = 1,
             radius = ~ (Online_percent-0.4)*100, popup = ~city  ,color = "green")
```

